---
name: Noushin Nabavi, PhD
position: "Economist, BC Ministry of Health"
address: "1515 Blanshard Street, Victoria, BC"
phone: +1 778-999-1982
www: noushinn.github.io
email: "nabavinoushin@gmail.com"
twitter: nabavinoushin
github: noushinn
linkedin: noushin-nabavi-56b27b13
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```



# Education
Degree: **Bachelor of Applied Science (B.Sc.), Cum Laude distinction**  
Field Of Study: Cellular and Molecular Biology  
University of Toronto (2001 – 2005)      
 
Degree: **Doctor of Philosophy (Ph.D.)**  
Field Of Study: Cell and Systems Biology  
University of Toronto (2006 – 2012)        
Thesis: Mobilization of Procollagen and Lysosomes during Osteoblast Stimulation with Ascorbic Acid, [UofT library](https://tspace.library.utoronto.ca/bitstream/1807/33894/1/Nabavi_Noushin_201206_PhD_thesis.pdf), 2012.  

**Certifications**:   
- Data Analytics using R, Data Camp and Coursera, Online, 2018-2021  
- Project Management and Agile Transformation, Mitacs Inc., University of British Columbia, 2017-2019  
- Teaching best practices, Yale Centre for Integration of Teaching and Learning, 2018  
- Certificate Program in Advanced Teaching and Learning at University of British Columbia, 2018
- Business Administration for Academics, mini-MBA, University of British Columbia, 2018  

# Professional Experiences

1: **Economist** at Pharmaceutical Analytics Unit, Health System Information and Reporting  
BC Ministry of Health, Victoria, BC, Canada, December 2020 - Present     
* Develop product listing agreement rebates using SQL and R programming;  
* Generate budget impact analysis for PharmaCare drug listings   

2: **Canadian Mitacs Science Policy Fellow** at Research Branch, Partnership and Innovation Division  
BC Ministry of Health, Victoria, BC, Canada, September 2019 - November 2020     
* Link health administrative data to replicate and extend surgical quality outcome reporting;   
* Enable program and policy evaluations through developing administrative data analytic workflows   
  
3: **Canadian Mitacs Science Policy Fellow** at Digital Platforms and Data Division   
BC Ministry of Citizens' Services, Victoria, BC, Canada, September 2018 - September 2019      
 Analyze and communicate complex administrative integrated data for evidence based policy making;   
* Build and strengthen effective stakeholder relationships with ministry clients and contractors;   
* Manage a data science project while developing and implementing timely methodologies and performance metrics  
  
4: **Senior Research Fellow** at Department of Experimental Medicine and Urologic Sciences  
University of British Columbia, Vancouver, BC, Canada, February 2015 - February 2018      
* Assemble and lead an international consortium of scientists for a genomics project, published 5 manuscripts and presented the results in 3 international conferences and 2 local symposia   
* Analyze and integrate genomics, transcriptomics, and proteomics datasets using R and proprietary softwares    
* Wrote and secured a $275K operating grant from BC Cancer Foundation for next generation sequencing tumor profiling of malignant peritoneal mesothelioma   

5: **Postdoctoral Fellow** at Department of Cellular and Molecular Pharmacology   
University of California, San Francisco, San Francisco, CA, USA, August 2013 - December 2014   
* Design research project and conduct experiments related to liver disease with an expert team of scientists;  
* Analyze experimental data and integrate results to generate presentations and publications;   
* Contribute to securing a $427K NIH grant  

6: **Siebel Stem Cell Fellow** at Department of Nutritional Sciences & Toxicology   
University of California, Berkeley, Berkeley, CA, USA, January 2012 - July 2013    
* Implement a reproducible scientific workflow for a project related to aging: designed and carried out experiments with animal models for aging, analyzed results;    
* Manage a research project with graduate students and undergraduate students towards publication in a peer-review journal  

7: **Teaching Assistant and Research Co-Supervisor**, Cell and Systems Biology
University of Toronto, Toronto, ON, Canada, September 2005 - December 2011   
* Rank the top 10% among departmental teaching assistants for 500+ hours of instruction in introductory biology laboratory, cellular molecular biology, and microbiology;   
* Create and delivere departmental lectures to 500+ students with satisfactory responses from students;  
* Co-supervise 10 undergraduate thesis students on successful thesis projects maintaining 100% retention rate (8 students secured successful science jobs, 2 pursued graduate studie)


# Awards and recognitions

1: Canadian Mitacs Science Policy Fellowship at  UVic/BC Ministry of Health, Victoria, BC,  2019-2020   
2: Finalist team for BC Premier’s Award in Evidence-Based Design for Children and Youth Mental Health Integrated data project at BC Ministry of Citizens' Services, Victoria, BC, 2019   
3: Third place for designing prosthetic hand tools at Health and Regenerative Medicine Hackathon (donation of award to Victoria Hand Project) at University of Victoria, Victoria, BC, 2019  
4: People’s choice leadership award for Victoria Code.Hack health hackathon at Island Health at Vancouver Island Hospital, Victoria, BC,  2019   
5: Canadian Mitacs Science Policy Fellowship at UVic/BC Ministry of Citizens' Services, Victoria, BC  2018-2019    
6: Travel award to participate and lead an analytics team for hackseq hackathon at University of British Columbia, Vancouver, BC,  2018-2019   
7: Travel award to participate at UBC’s career panel discussing role of postdocs in industry at University of British Columbia, Vancouver, BC,  2018   
8: Health and Regenerative Medicine Hackathon in kind value in mentorship award at University of Victoria, Victoria, BC,  2018    
9: Honorable mention for Brief Policy Pitch for Indigenous reconciliation at Institute of Public Administration, Victoria, BC,  2018   
10:  Certificate of distinction for completing Summer Institute for Evidence-Based STEM Teaching from The CIRTL Network,  on-line,   2018     
11: Entrepreneurship@UBC venture building phase 1 at University of British Columbia, Vancouver, BC,  March-May 2018  
12: Mitacs Accelerate Postdoctoral Fellowship Award at University of British Columbia, Vancouver, BC,  2015-2018     
13: Mini-MBA award, Partnership with Graduate Management Consulting Association at University of British Columbia, Vancouver, BC,  2018   
14: Rare Genomics Institute’s BeHEARD Technology Prize in partnership with Addgene at University of British Columbia, Vancouver, BC,  2017-2018   
15: Travel award to attend the American Association of Cancer Research conference at Washington DC, USA,  2017      
16:  Amazon Web Services Cloud Research Grant at University of British Columbia, Vancouver, BC,  2016-2017    
17:  Science Teaching Fellowship for the American Society for Microbiology,   on-line,    2014-2015     
18:  Siebel Stem Cell Postdoctoral Fellowship, University of California Berkeley,  California, USA,  2012-2013   
19:  Graduate Student Research Award at University of Toronto, July 2010   
20:  Travel Award from 15th Canadian Connective Tissue Conference,  Calgary, AB,  July 2009    
21:  Natural Sciences and Engineering Research Council (NSERC)-CGS at University of Toronto, Toronto, ON,  May 2009-2012    
22:  Ontario Textbook and Technology Grant at University of Toronto, Toronto, ON, December 2008   
23:  General Motors Women in Science and Mathematics Award at University of Toronto, Toronto, ON,  April 2008  
24:  Travel Award from 14th Canadian Connective Tissue Conference at McGill University, Montreal, QC,  June 5-7, 2008  
25:  Travel Award from the American Society for Cell Biology, 47th annual meeting,  San Diego, CA, USA,  December 2007  
26:  Queen Elizabeth II Aiming for the Top Tuition Scholarship at University of Toronto, Toronto, ON, September 2001   

# Publications
```{r publications}
knitr::write_bib(c("forecast", "vitae", "ggquiver", "naniar", "taipan"), "packages.bib")
bibliography_entries("noushin.bib", "Publications") %>%
  arrange(desc(issued)) 
```